---
title: "課堂練習模版"
author: "Hsu"
date: "2021-01-03"
output: output_format
params:
  id: "410683018"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Your code

```{r}
#if(){}
#if+conditional expression+programming blog

set.seed(10739)
customers <- data.frame(
  bills = sample(200:500, 10),
  vouchers = sample(c(T,F), size=10, replace=T,#replace使T F抽出後可放回
                     prob=c(0.4,0.6)
                     )
)
head(customers)
```
```{r}
bill <- customers$bills[[3]]
hasVoucher <- customers$vouchers[[3]]
totalBill <- 
{
  startingBill <- bill
  if(hasVoucher)
  {
    bill <- bill - 20
  }
  message("You initial bill is ", startingBill,".\n",
          "You final bill is ", bill)
  bill
}
print(totalBill)
```
```{r}
get_totalBill <- function(bill, hasVoucher)
{
  startingBill <- bill
  if(hasVoucher)
  {
    bill <- bill - 20
  }
  message("You initial bill is ", startingBill,".\n",
          "You final bill is ", bill, "\n")
  bill
}
```
```{r}
get_totalBill(customers$bills[[6]],customers$vouchers[[6]])
```
```{r}
library(purrr)
map(
  1:10,
  ~{get_totalBill(customers$bills[[.x]],customers$vouchers[[.x]])})
```


```{r}
#新東西
purrr::map2(
  customers$bills, customers$vouchers,
  ~{get_totalBill(.x, .y)}
)
```
```{r}
f <- function(x){
  if(x<0)
  {
    stop("x has to be non-negative.")#終止城市繼續執行，但無法被回存
  }
  sqrt(x)#開根號
}
```
```{r}
f(-2)
f(2)
```
```{r}
comment_grade <- function(grade){
  if(grade < 60) {return("Don't give up. There is still hope.")}
  return("Good job. Keep going")#回存且又可達到stop想要的效果
}
```
```{r}
df_grades <- data.frame(
  grade=sample(50:95, 20, replace = T)
)
purrr::map_chr(    #如同unlist(map())，不過需要字串長度一樣
  df_grades$grade,
  comment_grade
) -> df_grades$comment
```
#5.2.2遇到多個旗標
```{r}
grades <- c(55, 72, 40) # fail in first
# any one failed? 
if(grades < 60) {message("\nYes, someone failed")}
#只看了第一個數字
```
```{r}
grades <- c(72, 55, 40) # fail in second
# any one failed? 
if(grades < 60) message("\nYes, someone failed")
```
#Use

all() to flag if all failed. #everyopne failed

any() to flag if any failed. #someone failed

```{r}
grades <- c(72, 55, 82)
# any one failed? 
if(any(grades < 60)) message("\nYes, someone failed")
```
```{r}
#環境設定長度為1
Sys.setenv("_R_CHECK_LENGTH_1_CONDITION_" = "true")
```
```{r}
#因為上面的設定而出現error
grades <- c(55, 72, 82)
# any one failed? 
if(grades < 60) message("\nYes, someone failed") # error now
```
#&& ||
When using logical operations on logical values:

To judge if all conditions hold, a proper flag should be from && than &. #&&會依序檢查只要遇到一格F就會停

```{r}
grades >= 60
gender == "female"
(grades >= 60) & (gender == "female") #and
```


To judge if any condition hold, a proper flag should be from || than |. # ||在condition更有效率
```{r}
(grades >= 60) | (gender == "female") #or
```

```{r}
grade1 <- list(
  economics=55,
  calculus=77
)
grade2 <- c(
  economics=55,
  calculus=77
)
```

```{r}
(is.list(grade1) &  grade1$economics > 60)
(is.list(grade2) &  grade2$economics > 60)
```

```{r}
(is.list(grade1) && grade1$economics > 60)
(is.list(grade2) && grade2$economics > 60)
```
```{r}
myAge <- 75

if(myAge >=65 | stop("Error")){
  "Qualified"
} else {
  warning("Not qualified")
}
```
```{r}
if(myAge >=65 ||  stop("Error")){
  "Qualified"
} else {
  warning("Not qualified")
}
```
#When designing a control flow, the outcome from conditions should:

Always generate ONE flag signal.

Its AND/OR operators should be sequential (ie. using &&/||) to avoid unnecessary errors and boost computation efficiency

#5.2.4if else
```{r}
# 前提條件
x <- 4L
# 任務
fx <- {
  
  # ending scenario 1:
  {
    x/2
  }
  # ending scenario 2:
  {
    -(x+1)/2
  }
}
```

```{r}
# 前提條件
x <- 4L #整數
# 任務
fx <- {
  
  # ending scenario 1:
  if(x %% 2 ==0)
  {
    x/2
  } else
  # ending scenario 2:
  {
    -(x+1)/2
  }
}

fx
```
#else must follow } immediately in the same line as

} else
Otherwise, the preceeding if(...){...} will be considered a complete if-control flow.

```{r}
fx <- function(x)
{
  # ending scenario 1:
  if(x %% 2 ==0)
  {
    return(x/2)
  } else
  # ending scenario 2:
  {
    return(-(x+1)/2)
  }
}
```
```{r}
fx(4L)
fx(7L)
```
#5.2.5 if-else if-else if-else
```{r}
# 前提
grade <- 88
# 任務
comment <- 
{
  {
    "優"
  }
  {
    "良"
  }
  {
    "尚可"
  }
  {
    "待加強"
  }
}
```

```{r}
# 前提
grade <- 88
# 任務
comment <- 
{
  if(grade>=90)
  {
    "優"
  } else
  if(grade >=80 && grade <=89)
  {
    "良"
  } else
  if(grade>=70 && grade <=79)
  {
    "尚可"
  } else
  {
    "待加強"
  }
}

comment
```

```{r}
comment_grade <- function(grade){
  if(grade>=90)
  {
    "優"
  } else
  if(grade >=80 && grade <=89)
  {
    "良"
  } else
  if(grade>=70 && grade <=79)
  {
    "尚可"
  } else
  {
    "待加強"
  }
}

comment_grade(65)
```
#If there are multiple TRUE flags (所有條件沒有互相互斥)from different if-condition expressions, ONLY the programming block follows the FIRST TRUE flag will be executed
```{r}
comment_grade <- function(grade){
  if(grade>=85)
  {
    "優"
  } else
  if(grade >=80 && grade <=89)
  {
    "良"
  } else
  if(grade>=70 && grade <=79)
  {
    "尚可"
  } else
  {
    "待加強"
  }
}

comment_grade(86)
```

