---
title: "課堂練習模版"
author: "Hsu"
date: "2021-01-09(2)"
output: output_format
params:
  id: "410683018"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Your code
#while loop
```{r}
# iterates: 1,2,3,4,5
# iteration block
{
  sampleData[[.x]]
}
```

```{r}
.x <- .x + 1 # if .x exists in your environment
#(count <- count +1) count是計算之意

```

```{r}
flag <- (.x < 5) # continuation flag condition with definite iterates
```
```{r}
while(flag)#while flag is true then keep continue
{
  .x <- .x+1 # Iterate generation
  sampleData[[.x]][[1]]
  flag <- (.x < 5) # Continuation flag
}
```
#真正流程
```{r}
rm(list=ls())
sampleData <- list(
  list("男", 45), list("女", 32), list("男",50), list("男",33), list("女", 21)
)

.x <- 0 # initial iterate
flag <- TRUE # initial flag
while(flag)
{
  .x <- .x+ 1 # Iterate generation
  print(sampleData[[.x]][[1]])
  flag <- (.x < 5) # continuation flag
}
```
```{r}
#比較
for(.x in 1:5)
{
  print(sampleData[[.x]][[1]])
}
```
#Safe guard while-loop(限制跑的數量)
```{r}
.x <- 0 # initial iterate
flag <- TRUE # initial flag
cat('Iterate .x starts at 0, and continue to\n')
while(flag && .x <= 100) # throw in maximal iterate restriction
{
  .x <- .x+ 1 # Iterate generation
  print(sampleData[[.x]][[1]])
  flag <- (.x < 5) # continuation flag 
  cat('.x = ', .x, ' complete\n')
}
```
#Guess Number例題
Computer randomly drawed a number from 10 to 50, denoted as x0. If user guesses a number less than x0, show “Higher” on the screen. If larger than x0, show “Lower” on the screen. When guess incorrectly, user can guess again until guessing correctly, then prompt “BINGO!!! You guess it right after XXX trials” on the screen where XXX is number of iterations have taken
```{r}
# computer pick a number
.computerPick <- {
  
}

# iteration time
.x <- 1

# user guess
userGuess <- readline("What's your guess?")

# conditional execution of 3 blocks
{
  "Higher"
}
{
  "Lower"
}
{
  glue::glue("BINGO!!! You guess it right after {.x} trials")
}
```

```{r}
# computer pick a number
.computerPick <- {
  sample(10:50, 1)
}


# iteration block
{
  # iteration generation
  # # iteration time
  # .x <- 1

  # user guess
  userGuess <- readline("What's your guess?")

  # conditional execution of 3 blocks
  result <-
    if (as.integer(userGuess) < .computerPick) {
      "Higher"
    } else
    if (as.integer(userGuess) > .computerPick) {
      "Lower"
    } else {
      glue::glue("BINGO!!! You guess it right after {.x} trials")
    }

  message(result)
  
  # continuation flag
  
}
```
```{r}
# computer pick a number
.computerPick <- {
  sample(10:50, 1)
}

# iteration time
.x <- 0
flag <- T
while(flag)
# iteration block
{
  # iteration generation
  .x <- .x + 1
  
  # user guess
  userGuess <- readline("What's your guess?")

  # conditional execution of 3 blocks
  result <-
    if (as.integer(userGuess) < .computerPick) {
      "Higher"
    } else
    if (as.integer(userGuess) > .computerPick) {
      "Lower"
    } else {
      glue::glue("BINGO!!! You guess it right after {.x} trials")
    }

  message(result)
  
  # continuation flag
  flag <- ! stringr::str_detect(result, "BINGO")
}
```

